### 2021-10-29 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.75\linewidth]{figures/simulation_results}
		\caption{Results from the simulation study. We simulated pathogen and non-pathogen (host \& environmental) effects on the spVL trait under the POUMM with different trait heritability values (y-axis) and selection strengths (x-axis). For each simulated dataset, we applied our method to estimate the non-pathogen effects and performed GWAS using these estimates. (A) shows how well we can estimate the host effect using our method (left side) compared to just the scaled trait value (right side). (B) shows how GWAS can theoretically be improved by using the true (normally unknown) non-pathogen effects on spVL (left). It can still be improved in certain scenarios using our estimate for this value (middle) compared to the current standard - using just the (scaled) trait value (right). Tile color represents the average value over 20 simulated datasets of 500 samples for each heritability and selection strength value. The black point represents our estimates for the heritability and selection strength of spVL based on Swiss data. RMSE = Root mean square error, TPR = True positive rate.}
		% (RMSE) with respect to simulated values for the host part of spVL ($\bm{{g_h}}$) as a function of spVL trait heritability and selection strength on the trait. The left plot is for the POUMM-based estimate of the non-pathogen part of the trait ($\bm{\hat{e}}$) and the right plot is for the raw trait value scaled by the mean trait value, such that it is centered at zero ($\bm{z} - \bm{\bar{z}}$). (B) True positive rate (TPR) in GWAS performed using true (simulated) values for the non-pathogen part of the trait ($\bm{e}$), the POUMM-based estimate for the non-pathogen part of the trait ($\bm{\hat{e}}$), and the raw trait value scaled by the mean trait value ($\bm{z} - \bm{\bar{z}}$). The color of each plot tile in (A) and (B) represents the average value over 20 simulated datasets of 500 samples. The black point shows our estimates for the heritability of and selection strength on the spVL trait based on Swiss data.}
		\label{fig:simulationResults}
	\end{center}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.75\linewidth]{figures/simulation_results}
		\caption{Results from the simulation study. We simulated pathogen genetic effects, host genetic effects, and environmental effects on the spVL trait under the POUMM with different trait heritability values (y-axis) and selection strengths (x-axis). For each simulated dataset, we applied our method to estimate the non-pathogen effects (host genetic \& environmental effects) and performed GWAS using these estimates. (A) shows how well we can estimate the host genetic effect using our method (left) compared to the whole trait value (scaled such that it has mean 0) (right). (B) shows the theoretical improvement to GWAS using the true, simulated non-pathogen effect on spVL (left) and using our estimate for this value (middle) in different simulated scenarios. For comparison, we show GWAS results using the whole trait value (right). Each tile's color corresponds to the average value across 20 simulated datasets of 500 samples for each heritability and selection strength value. The black point represents our estimates for the heritability and selection strength of spVL based on Swiss data. RMSE = Root mean square error, TPR = True positive rate.}
		\label{fig:simulationResults}
	\end{center}
\end{figure}
